\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-08 Limber_Comment.tex
Started on Peters comments

\begin{abstract}
Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to explain away the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.  Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

The measurement of weak gravitational lensing by large scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.  As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys. Interest in the results from these surveys is high as statistically significant deviations have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{hildebrandt/etal:2016} and the Canada-France-Hawaii Telescope Lensing Survey \citep[CFHTLenS;][] {joudaki/etal:2016}.  If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological models need to be considered.  \citet{joudaki/etal:2017} have shown, for example, that the tension can be resolved with an evolving dark energy model.

In this comment paper we discuss the flat sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function. The Limber approximation for cosmic shear has been previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies. Recently, however, \citet{kitching/etal:2016} reported that when considering the flat sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced. They demonstrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.

This comment discusses why we disagree with the findings of \citet{kitching/etal:2016} and is structured as follows.  In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.  We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.  In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for cosmic shear power spectrum.

>>>>

\begin{abstract}
Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to significantly reduce the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.  Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

The measurement of weak gravitational lensing by large-scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.  As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys. Interest in the results from these surveys is high as statistically significant deviations have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{hildebrandt/etal:2016} and the Canada-France-Hawaii Telescope Lensing Survey \citep[CFHTLenS;][] {joudaki/etal:2016}.  If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological models need to be considered.  \citet{joudaki/etal:2017} have shown, for example, that the tension can be resolved with an evolving dark energy model.

In this comment paper we discuss the flat-sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation functions. The Limber approximation for cosmic shear was previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies. Recently, however, \citet{kitching/etal:2016} reported that when considering the flat-sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced. They illustrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.    On initial inspection we found that these claims appeared implausible, for two reasons: First, in a naive estimate, the deviation of flat-sky approximation from a full treatment are expected to be of similar order as the fractional difference between $\theta_{\rm max}$ and $\sin\theta_{\rm max}$,
where $\theta_{\rm max}$ is the maximum angular scale considered in the cosmic shear analysis. In the case of \citep{hildebrandt/etal:2016}, where $\theta_{\rm max}=50$ arcmin, $(\theta_{\rm max} - \sin\theta_{\rm max})/\theta_{\rm max} \approx 3.52 \times 10^{-5}$.  Second, it was shown in \citet[][see their Fig.3]{giannantonio/etal:2012} that the difference between the Limber approximation and exact treatment is far smaller than cosmic variance, even for a full-sky cosmic shear survey.

This comment seeks to explore the content of \citet{kitching/etal:2016} in detail, discussing why we disagree with their findings.  It is structured as follows.  In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.  We are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.  In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for cosmic shear power spectrum.

### 2016-12-08 cfhtlens.tex
Started on Peters comments

The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of PSF-Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.    Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
\begin{itemize}
\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.  The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.  They also showed that the impact of calibration selection biases, that were not considered in \citet{miller/etal:2013}, would have lead to the over-correction of multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
\end{itemize}
All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.  Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.  Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}. This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.   We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Baseline Limber Flat' (LF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.  These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).

@@

We note that \citet{kitching/etal:2016} have chosen to use their `Flat' approximation in their `Full' non-Limber analysis rather than a full spherical-sky solution.  The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.  As shown in Figure~\ref{fig:Cl_xi}, however, their chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution. We do not find this to be the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.

@@

From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   
If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

@@

\subsection{On the Validation of Methods on Simulations}
It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.  We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.  It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.  Going beyond flat sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large scale under-estimation of power varies with the simulation box size. This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\rm{Mpc/h}$ to 515$\rm{Mpc/h}$ \citep[see Fig. 5 in][]{harnois-deraps/vanwaerbeke:2015}. The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.

@@

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.  For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.  The size of the pre-factor, averaged over this range, is of the order of 0.01\%. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%). The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.

>>>>

The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of PSF-Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.    Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
\begin{itemize}
\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.  The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.  They also showed that the impact of calibration selection biases, that were not considered in \citet{miller/etal:2013}, would have lead to the over-correction of multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
\end{itemize}
All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.  Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.  Until this analysis is complete we note that these known shortcomings with the original CFHTLenS results impact in different ways on the cosmological conclusions that one can draw from the survey.

\citet{kitching/etal:2016} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}. This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.   We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Baseline Limber Flat' (LF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.  These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).

@@

We note that \citet{kitching/etal:2016} use their `Flat' approximation for the `Full' non-Limber analysis of the CFHTLenS data.   This is because on a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.   In Figure~\ref{fig:Cl_xi}, however, we show that this chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution in the Limber approximated case.  This is not the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.  We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function.

@@

From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   
If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

@@

\subsection{On the Validation of Methods on Simulations}
It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.  We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.  It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.  Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size. This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\rm{Mpc/h}$ to 515$\rm{Mpc/h}$ \citep[see Fig. 5 in][]{harnois-deraps/vanwaerbeke:2015}. The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.

@@

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.  For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.  The size of the pre-factor, averaged over this range, is of the order of 0.01\%. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%). The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.

### 2016-12-08 theory.tex
Started on Peters comments

\subsection{The Flat-Sky approximation and Extended Limber Approximation}
The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}, given by
\be
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\ee
where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation \citep{limber:1953} as,
\be 
P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu(\ell)}{f_K(\chi)},\chi \right).
\label{eqn:Pkappa} 
\ee
Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.   The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}, and the value of $\nu(\ell)$ depends on whether a baseline Limber approximation, $\nu(\ell) = \ell$, or the more accurate extended Limber approximation, $\nu(\ell) = \ell + 0.5$, from \citet{loverde/afshordi:2008} is used.   \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
\be
T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} \, .
\label{eqn:Tl}
\ee
The corresponding pre-factor for the convergence power spectrum, along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum, is given in \citet{jk12}.

@@

Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.   The Standard and Spherical models agree at the few percent level above $\ell>10$ and below $\theta< 100$ arcmin.  The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.    We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.    To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.

@@

Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in many theoretical codes over the years.  Instead these codes have evolved to account for (much more) important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.    Two exceptions to this are recent updates to CLASS \citep{blas/lesgourgues/tram:2011,audren/etal:2013} and CosmicFish \citep{raveri/etal:2016}.  On-going code comparisons have, however, revealed differences that are larger than the expected impact of Limber or non-Limber approximation.   We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.   Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions about the impact of this effect.

>>>>

\subsection{The Flat-Sky approximation and Extended Limber Approximation}
The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}, given by
\be
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\ee
where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation \citep{limber:1953} as,
\be 
P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu(\ell)}{f_K(\chi)},\chi \right).
\label{eqn:Pkappa} 
\ee
Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.   The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}, and the value of $\nu(\ell)$ depends on whether a baseline Limber approximation, $\nu(\ell) = \ell$, or the more accurate extended Limber approximation, $\nu(\ell) = \ell + 0.5$, from \citet{loverde/afshordi:2008} is used.   \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
\be
T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, .
\label{eqn:Tl}
\ee
The corresponding pre-factor for the convergence power spectrum, along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum, is given in \citet{jk12}.

@@

Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.   The Standard and Spherical models agree at the few percent level above $\ell>10$ and below $\theta< 100$ arcmin.  The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with
\be
T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 \approx 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
\ee    
We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.  By comparing the expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we see that the \citet{kitching/etal:2016} `Flat' Sky approximation effectively introduces a new term $2/\ell$ making it more deviant from the full spherical solution in comparison to the standard $T_\ell = 1$ case.    To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.

@@

Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in many theoretical codes over the years.  Instead these codes have evolved to account for critical approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.    Two exceptions to this are recent updates to CLASS \citep{blas/lesgourgues/tram:2011,audren/etal:2013} and CosmicFish \citep{raveri/etal:2016}.  On-going code comparisons have, however, revealed differences that are larger than the expected impact of Limber or non-Limber approximation.   We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.   Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions about the impact of this effect.
